Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/intro.tex
some intro tweaks

Code that handles untrusted inputs, such as processing network
data or parsing a file, is error-prone and is often exploited by
attackers.  This is in part because attackers have precise control
over the inputs to that code, and can craft inputs that trigger
subtle corner cases in input processing.  For example, the libpng image decompression
library has had 24 remotely exploitable vulnerabilities from 2007 to
2013~\cite{cvedetails:libpng},
and Adobe's PDF and Flash viewers have been notoriously
plagued by input processing vulnerabilities.  Even relatively
simple formats, such as those used by the zlib compression
library, have had input processing vulnerabilities in the
past~\cite{cvedetails:zlib}.

Typically, input parsers, particularly for binary formats, are often
written by hand. Not only is such code plagued by the bugs mentioned above, but
two separate hand-written implementations of the same protocol might disagree on
the meaning of a particular input, which can lead to security
vulnerabilities~\cite{saurik-masterkey}.

@@

First, parser generators typically parse inputs into an abstract syntax
tree (AST) that corresponds to the grammar.  In order to produce a data
structure that the rest of the application code can easily process,
application developers must write explicit {\em semantic actions} that
update the application's internal representation of the data based on
each AST node.  Not only does the programmer allocate memory and manipulate pointers,
 operations that are error-prone, but
writing these semantic actions
also requires the programmer to describe the structure of the input three
times---once to describe the grammar, once to describe the internal data
structure, and once again in the semantic actions that translate the
grammar into the data structure---leading to another potential source
of bugs and inconsistencies.

Second,  applications often need to produce output in the same
format as their input---for example, applications might both
read and write files, or both receive and send network packets.
Most parser generators focus on just parsing an input, rather
than producing also an output, thus requiring the programmer to manually
construct outputs, which is work-intensive and more code that could contain errors.
Some parser generators, such as
Boost.Spirit~\cite{boost-spirit},
allow reusing the grammar for generating output from the internal
representation.  However, those generators require yet another set of
semantic actions to be written, transforming the internal representation
into an AST\@.

>>>>

Code that handles untrusted inputs, such as processing network
data or parsing a file, is error-prone and is often exploited by
attackers.
%   This is in part because attackers have precise control
% over the inputs to that code, and can craft inputs that trigger
% subtle corner cases in input processing.
For example, the libpng image decompression library had 24 remotely
exploitable vulnerabilities from 2007 to 2013~\cite{cvedetails:libpng},
Adobe's PDF and Flash viewers have been notoriously plagued by input
processing vulnerabilities, and even the zlib compression library had
input processing vulnerabilities in the past~\cite{cvedetails:zlib}.
With a memory-unsafe language like C, mistakes in input processing
code can lead to memory errors like buffer overflows, but even with
a memory-safe language like Java, inconsistencies between different
parsers can lead to security issues~\cite{saurik-masterkey}.

@@

First, parser generators typically parse inputs into an abstract syntax
tree (AST) that corresponds to the grammar.  In order to produce a data
structure that the rest of the application code can easily process,
application developers must write explicit {\em semantic actions} that
update the application's internal representation of the data based on
each AST node.  
Writing these semantic actions requires the programmer to describe the
structure of the input three
times---once to describe the grammar, once to describe the internal data
structure, and once again in the semantic actions that translate the
grammar into the data structure---leading to potential bugs and
inconsistencies.
Furthermore, in a memory-unsafe language like C, these semantic
actions often involve error-prone manual memory allocation and
pointer manipulation.

Second,  applications often need to produce output in the same
format as their input---for example, applications might both
read and write files, or both receive and send network packets.
Most parser generators focus on just parsing an input, rather
than producing an output, thus requiring the programmer to manually
construct outputs, which is work-intensive and more code that could contain errors.
Some parser generators, such as
Boost.Spirit~\cite{boost-spirit},
allow reusing the grammar for generating output from the internal
representation.  However, those generators require yet another set of
semantic actions to be written, transforming the internal representation
back into an AST\@.
